Supplementary Material for 'The complex network of trophic interactions in

### 2023-06-29 MS_ToSubmit/MS_Burdwood_foodweb.tex
Changes on Acanthoserolis & Aega sp

\usepackage{lineno} % add
  \linenumbers % turns line numbering on

@@

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

@@

@@

    \author[]{Marcos Tatián\textsuperscript{h,i}%
  %
  }

    \author[]{Diego Urteaga\textsuperscript{j}%
  %
  }

@@

      \affiliation[1]{Centro Austral de Investigaciones Cientificas
(CADIC-CONICET), Argentina}
    \affiliation[2]{Instituto Antartico Argentino (IAA), Argentina}
    \affiliation[3]{Instituto de Ciencias Polares, Ambiente y Recursos
Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina}
    \affiliation[4]{Facultad de Ciencias Exactas y Naturales,
Universidad de Buenos Aires (UBA), Argentina}
    \affiliation[5]{Instituto de Biodiversidad y Biologia Experimental y
Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina}
    \affiliation[6]{Instituto de Investigaciones Marinas y Costeras
(IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina}
    \affiliation[7]{Wildlife Conservation Society, Argentina}
    \affiliation[8]{Facultad de Ciencias Exactas, Fisicas y Naturales,
Universidad Nacional de Cordoba (UNC), Argentina}
    \affiliation[9]{Instituto de Diversidad y Ecologia Animal
(IDEA-CONICET)}
    \affiliation[10]{Museo Argentino de Ciencias Naturales ``Bernardino
Rivadavia'', Argentina}
    \cortext[cor1]{Corresponding author}

  \begin{abstract}
  Globally, the total area of the world ocean designated under marine
  protection has increased in the recent decades. The majority of these
  Marine Protected Areas (MPAs) focus on the presence of particularly
  vulnerable, keystone, or charismatic species, large numbers of endemic
  species, and/or high biodiversity across taxonomic levels. In the
  sub-Antarctic region, the level of ocean protection is mainly
  associated to oceanic islands, except for the MPAs Namuncurá -
  Burdwood Bank I and II (MPA N-BB, 53º--55ºS and 56º--62ºW,
  respectively), which are associated to a submarine plateau and its
  southern adjacent deep slope region, respectively. Here, we present
  the first detailed analysis of the network of predator-prey
  interactions (food web) for the MPA N-BB ecosystem. We applied a
  network approach to characterise the food web in terms of complexity
  and structure, and identifying the species' role in such a framework.
  In terms of complexity, the MPA N-BB food web consisted of 1780
  predator-prey interactions and 375 species, with a link density of
  4.75 and a connectance of 0.01. In terms of structure, almost half of
  the consumers were omnivores (0.48), and the network displayed a
  small-world pattern. These findings suggest that the ecosystem might
  be vulnerable to external perturbations targeting highly connected
  species, although structural properties might provide resilience and
  resistance, resulting in a rearranged structure that preserves its
  original functions. Furthermore, we identified several species as
  important in terms of different aspects of trophic structure and
  functioning, and response to perturbations. We suggest that generalist
  species, mainly fishes, play a crucial role in the ecosystem's
  bentho-pelagic coupling process and that other species, besides the
  longtail southern cod \emph{Patagonotothen ramsayi} and the Fueguian
  sprat \emph{Sprattus fuegensis}, should be considered as relevant
  energy transfers for the ecosystem. Finally, we argue that the
  diversity of species, including both the benthic and pelagic habitats,
  is responsible for seccuring the connectivity within the food web
  against perturbations, therefore contributing to the structure and
  stability of the ecosystem.
  \end{abstract}
    \begin{keyword}
    Food web \sep Complexity \sep Structure \sep Burdwood Bank \sep 
    Southwest Atlantic
  \end{keyword}

@@

\toprule()

@@

\midrule()

@@

@@

\bottomrule()

@@

In terms of complexity, the MPA Namuncurá - Burdwood Bank food web (N-BB
I and II) consisted of 1780 predator-prey interactions and 375 species,
where 93\% of them were defined at the species taxonomical level (Figure
2, Table S2). The food web presented a link density (e.g., the average
number of interactions per species) of 4.75, and a connectance of 0.01.
Almost half of the consumers were omnivores (0.48), feeding on sources
at different trophic levels. The food web displayed a small-world
pattern, meaning that the path length was lower and the clustering
coefficient higher than the random networks (Table 2).

@@

\caption{\label{tab:table2}Network-level properties of the MPA Namuncurá - Burdwood Bank food web. CPL: Characteristic Path Length; CC: Clustering Coefficient; SW: Small-World pattern. See table 1 for definitions and ecological relevance.}
\centering
\begin{tabular}[t]{r|r|r|r|r|r|r|l}
\hline
\textbf{Species} & \textbf{Interactions} & \textbf{Density} & \textbf{Connectance} & \textbf{Omnivory} & \textbf{CPL} & \textbf{CC} & \textbf{SW}\\
\hline
375 & 1780 & 4.75 & 0.01 & 0.48 & 2.96 & 0.08 & True\\
\hline
\end{tabular}
\end{table}

The degree distribution of the food web showed an asymmetric frequency
in the number of interactions, where most of the species had a
relatively low number of interactions and few species concentrated most
of them (Figure 3A). The distribution of prey among predators showed
that most consumers fed on a low number of prey whereas few had multiple
prey (Figure 3B). The top-five predators in number of prey were:
yellowfin notothen \emph{Patagonotothen guntheri} (Notothenioid fish, 50
prey), rock cod \emph{Patagonotothen ramsayi} (Notothenioid fish, 49
prey), broad nose skate \emph{Bathyraja brachyurops} (Chondrichthyan, 33
prey), Patagonian toothfish \emph{Dissostichus eleginoides}
(Notothenioid fish, 30 prey), and graytail skate \emph{Bathyraja
griseocauda} (Chondrichthyan, 28 prey). Following the same distribution
pattern, few prey presented multiple predators (Figure 3C). The top-five
prey in number of predators were: Detritus (Non-living, 155 predators),
the three categories of Diatoms considered (benthic, centric and
pennate, 75 predators on average), and species of the genus
\emph{Euphausia} (Zooplankton, 47 predators). Finally, taking into
account the interactions within each functional group, most interactions
were concentrated in a few species (Figure 3D). The most evident species
were: \emph{Doryteuthis gahi} (Cephalopoda), \emph{Grimothea gregaria}
(Decapoda), \emph{Patagonotothen ramsayi}, \emph{Patagonotothen
guntheri} and \emph{Dissostichus eleginoides} (bentho-pelagic fish),
\emph{Sprattus fuegensis} and \emph{Micromesistius australis} (pelagic
fish), and species of \emph{Euphausia} and \emph{Themisto gaudichaudii}
(Zooplankton). Overall, there is an evident asymmetry in the
distribution of interactions among species at different levels in the
MPA N-BB food web.

@@

Notably, species of mid-TLs (3-4.2) showed the highest values of
betweenness, meaning that those species participated in the highest
number of shortest paths between species (Figure 4A). The following are
the species with the highest values: \emph{Patagonotothen ramsayi},
\emph{Salilota australis}, \emph{Dissostichus eleginoides} (fishes),
\emph{Doryteuthis gahi} (Cephalopoda), and \emph{Patagonotothen
guntheri} (Notothenioid fish) (Table S3).

Considering the topological role, `module specialist' species were the
most frequent and presented a wide TL range (1 - 4.7), as well as
`module hub' species (TL = 1 - 4); `module connector' was constrained to
mid-TLs (2 - 3.86); and `network connector', the least frequent, had all
of its species in low-TLs (1 - 2), except for one with TL = 3.48 (Figure
4D, see Figure S2 for species' topological roles in a food web graph
framework). Here it is important to highlight the two latter topological
roles because they are responsible for linking modules and maintaining
the connectivity of the food web: 41 species (4 network connectors + 37
module connectors) from 19 different functional groups with a TL range =
1 - 3.86. The following were the four species with a network connector
role: detritus, benthic diatoms, Foraminifera and \emph{Patagonotothen
ramsayi}. The 37 species with a module connector role represented these
functional groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Hydrozoa
(as `Cnidaria\_benthic'), Copepoda, Cumacea, Decapoda, diatoms,
Echinodermata, fish (bentho-pelagic and demersal Osteichthyes, and
Chondrychthyes), Polychaeta, Porifera, Pycnogonida (as `Benthos\_Misc')
and zooplankton (see Supplementary Material Table S3 for the identity of
the species).

@@

\caption{Species-level properties by trophic level: (A) betweenness, (B) closeness, (C) trophic similarity, and (D) topological role. Each point represents a species. Linear regressions for betweenness ($y = 74.96x - 121.71, R^2 = 0.05, p-value < 0.01$), closeness ($y = 1.01e-05x - 9.48e-4, R^2 = 0.003, p-value = 0.14$) and trophic similarity ($y = -0.02x + 0.11 , R^2 = 0.08, p-value < 0.01$). Note that for panels A, B and C only species with TLs equal or greater than 2 were considered.}\label{fig:figure4}
\end{figure}

@@

Food web connectance is a feature that resumes the complexity of the
network, but more importantly, it is an emergent property of pairwise
species interactions (Poisot \& Gravel, 2014). It contains information
regarding how interactions within an ecological network are distributed
and predicts reasonably well key dynamical properties of ecological
networks (Dunne et al., 2002a). Complex marine food webs (i.e.~with more
than 25 trophic species) show connectance values ranging from 0.01 -
0.27 (Marina, Saravia, et al., 2018). In particular, food webs from
high-latitude regions tend to exhibit a connectance closer to the
minimum (between 0.01 and 0.05) (Kortsch et al., 2015; Rodriguez et al.,
2022; Santana et al., 2013). Whether food webs display a low or a high
connectance helps to better comprehend ecosystem's synthetic properties
like robustness. In this sense, empirical analyses support the notion
that highly-connected ecological networks are robust against external
perturbations such as the introduction of new (e.g., invasive) species
(Smith-Ramesh et al., 2017) as well as species removal (e.g., local
extinction) (Dunne et al., 2002b; Montoya \& Solé, 2003). The
connectance of the food web of the MPA Namuncurá - Burdwood Bank (0.01)
is one of the lowest reported so far for these regions; in particular,
it appears to much lower than that of Beagle Channel (0.05), an adjacent
coastal area (Rodriguez et al., 2022).

The degree distribution, the distribution of the number of interactions
per species, is the core of the structure of species interactions, which
influences the opportunities for multiple species to persist in the long
term and, therefore, their coexistence (Godoy et al., 2018). The food
web for the MPA N-BB presents an asymmetric degree distribution. This
pattern was identified at different levels of analysis: food web,
predator, prey, and functional group. Such asymmetry is a well-known
feature in empirical complex food webs in particular (Dunne et al.,
2002a; Montoya \& Solé, 2003; Stouffer et al., 2005), and has received
great attention in complex networks in general (Albert \& Barabási,
2002; Newman, 2003). The degree distribution affects the resilience of
complex food webs against random failures and pressure on a particular
component of the web: food webs showing right-skewed distributions, like
the one described in this study, are more vulnerable to the removal of
the most connected species or hubs, with the potential of producing
secondary extinctions and a catastrophic fragmentation of the network
(Albert et al., 2000; Dunne et al., 2002b; Eklöf \& Ebenman, 2006).

It is suggested that the small-world pattern, i.e., a network with short
path length and high clustering coefficient, is not frequent in complex
marine food webs, mainly due to a low clustering coefficient compared to
random networks (Dunne et al., 2002c; Marina, Saravia, et al., 2018).
However, the food web of the MPA N-BB does display a small-world
pattern. Consequences of this could be of great importance in
recognizing evolutionary paths and the vulnerability to perturbations
(Montoya \& Solé, 2002). On the one hand, a short path length implies a
rapid spread of an impact (e.g., contaminant, population fluctuation,
local extinction) throughout the network but, at the same time, more
potentially adaptive dynamics in the face of external perturbations
(Montoya \& Solé, 2002; Williams et al., 2002). On the other hand, a
high clustering coefficient indicates the formation of subnetworks
composed only by the neighbours of particular species. This translates
into a greater resistance of the network due to the confinement of
perturbations mainly within subnetworks and not spreading between them
(Heer et al., 2020; Kortsch et al., 2019). Overall, a small-world
topology provides ecological networks with greater resilience and
resistance (Bornatowski et al., 2017; Dormann et al., 2017).

@@

The degree distribution allows identifying important species, such as
potential keystone species (Dunne et al., 2002b; Solé \& Montoya, 2001),
generalist/specialist species, and dominant food sources (Kondoh et al.,
2010).

@@

Species' role can also be assessed in a module-based context. Among the
varying numbers of topological roles in which species can be divided,
two are remarkable: `module connector' and `network connector'. Here
again, the longtail southern cod \emph{Patagonotothen ramsayi} is
emphasized as an influential species for the connectivity of the food
web, which agrees with the suggested `wasp-waist' control for the MPA
N-BB ecosystem (Riccialdelli et al., 2020). But most importantly, our
results broaden this issue by pointing out that there are other species,
belonging to a wide range of trophic positions (1 to 3.86) and
representing 20 different functional groups, that should be considered.
Thus, we propose that the diversity of species (benthic and pelagic)
maintains the connectivity of the food web, therefore contributing to
the trophic structure and ecosystem's stability.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002a}{}}%
Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002a). Food-web
structure and network theory: {The} role of connectance and size.
\emph{Proceedings of the National Academy of Sciences}, \emph{99}(20),
12917--12922. \url{https://doi.org/10.1073/pnas.192407699}

\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002}{}}%
Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002b). Network
structure and biodiversity loss in food webs: Robustness increases with
connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567.
\url{https://doi.org/10.1046/j.1461-0248.2002.00354.x}

\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002b}{}}%
Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002c). \emph{Small
{Networks} but not {Small Worlds}: {Unique Aspects} of {Food Web
Structure}}. {Santa Fe Institute}.

>>>>

@@

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
% TODO: Currently lineno needs to be loaded after amsmath because of conflict
% https://github.com/latex-lineno/lineno/issues/5
\usepackage{lineno} % add
  \linenumbers % turns line numbering on
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}

@@

    \author[]{Laura Schejter\textsuperscript{h}%
  %
  }

@@

    \author[]{Marcos Tatián\textsuperscript{i,j}%
  %
  }

    \author[]{Diego Urteaga\textsuperscript{k}%
  %
  }

@@

      \affiliation[1]{Centro Austral de Investigaciones Cientificas
(CADIC-CONICET), Argentina}
    \affiliation[2]{Instituto Antartico Argentino (IAA), Argentina}
    \affiliation[3]{Instituto de Ciencias Polares, Ambiente y Recursos
Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina}
    \affiliation[4]{Facultad de Ciencias Exactas y Naturales,
Universidad de Buenos Aires (UBA), Argentina}
    \affiliation[5]{Instituto de Biodiversidad y Biologia Experimental y
Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina}
    \affiliation[6]{Instituto de Investigaciones Marinas y Costeras
(IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina}
    \affiliation[7]{Wildlife Conservation Society, Argentina}
    \affiliation[8]{Instituto Nacional de Investigacion y Desarrollo
Pesquero (INIDEP), Consejo Nacional de Investigaciones Cientificas y
Tecnicas (CONICET), Argentina}
    \affiliation[9]{Facultad de Ciencias Exactas, Fisicas y Naturales,
Universidad Nacional de Cordoba (UNC), Argentina}
    \affiliation[10]{Instituto de Diversidad y Ecologia Animal
(IDEA-CONICET)}
    \affiliation[11]{Museo Argentino de Ciencias Naturales ``Bernardino
Rivadavia'', Argentina}
    \cortext[cor1]{Corresponding author}

  \begin{abstract}
  Globally, the total area of the world ocean designated under marine
  protection has increased in the recent decades. The majority of these
  Marine Protected Areas (MPAs) focus on the presence of particularly
  vulnerable, keystone, or charismatic species, large numbers of endemic
  species, and/or high biodiversity across taxonomic levels. In the
  sub-Antarctic region, the level of ocean protection is mainly
  associated to oceanic islands, except for the MPAs Namuncurá -
  Burdwood Bank I and II (MPA N-BB, 53º--55ºS and 56º--62ºW,
  respectively), which are associated to a submarine plateau and its
  southern adjacent deep slope region, respectively. Here, we present
  the first detailed analysis of the network of predator-prey
  interactions (food web) for the MPA N-BB ecosystem. We applied a
  network approach to characterise the food web in terms of complexity
  and structure, and identifying the species' role in such a framework.
  In terms of complexity, the MPA N-BB food web consisted of 1788
  predator-prey interactions and 380 species, with a link density of
  4.70 and a connectance of 0.01. In terms of structure, almost half of
  the consumers were omnivores (0.48), and the network displayed a
  small-world pattern. These findings suggest that the ecosystem might
  be vulnerable to external perturbations targeting highly connected
  species, although structural properties might provide resilience and
  resistance, resulting in a rearranged structure that preserves its
  original functions. Furthermore, we identified several species as
  important in terms of different aspects of trophic structure and
  functioning, and response to perturbations. We suggest that generalist
  species, mainly fishes, play a crucial role in the ecosystem's
  bentho-pelagic coupling process and that other species, besides the
  longtail southern cod \emph{Patagonotothen ramsayi} and the Fueguian
  sprat \emph{Sprattus fuegensis}, should be considered as relevant
  energy transfers for the ecosystem. Finally, we argue that the
  diversity of species, including both the benthic and pelagic habitats,
  is responsible for seccuring the connectivity within the food web
  against perturbations, therefore contributing to the structure and
  stability of the ecosystem.
  \end{abstract}
    \begin{keyword}
    Food web \sep Complexity \sep Structure \sep Burdwood Bank \sep 
    Southwest Atlantic
  \end{keyword}

@@

\toprule\noalign{}

@@

\midrule\noalign{}

@@

\bottomrule\noalign{}
\endlastfoot

@@

@@

In terms of complexity, the MPA Namuncurá - Burdwood Bank food web (N-BB
I and II) consisted of 1788 predator-prey interactions and 380 species,
where 93\% of them were defined at the species taxonomical level (Figure
2, Table S2). The food web presented a link density (e.g., the average
number of interactions per species) of 4.70, and a connectance of 0.01.
Almost half of the consumers were omnivores (0.48), feeding on sources
at different trophic levels. The food web displayed a small-world
pattern, meaning that the path length was lower and the clustering
coefficient higher than the random networks (Table 2).

@@

\caption{\label{tab:table2}Network-level properties of the MPA Namuncurá - Burdwood Bank food web. CPL: Characteristic Path Length; CC: Clustering Coefficient; SW: Small-World pattern. See table 1 for definitions and ecological relevance.}
\centering
\begin{tabular}[t]{r|r|r|r|r|r|r|l}
\hline
\textbf{Species} & \textbf{Interactions} & \textbf{Density} & \textbf{Connectance} & \textbf{Omnivory} & \textbf{CPL} & \textbf{CC} & \textbf{SW}\\
\hline
380 & 1788 & 4.71 & 0.01 & 0.48 & 2.99 & 0.08 & True\\
\hline
\end{tabular}
\end{table}

The degree distribution of the food web showed an asymmetric frequency
in the number of interactions, where most of the species had a
relatively low number of interactions and few species concentrated most
of them (Figure 3A). The distribution of prey among predators showed
that most consumers fed on a low number of prey whereas few had multiple
prey (Figure 3B). The top-five predators in number of prey were:
yellowfin notothen \emph{Patagonotothen guntheri} (Notothenioid fish, 50
prey), rock cod \emph{Patagonotothen ramsayi} (Notothenioid fish, 49
prey), broad nose skate \emph{Bathyraja brachyurops} (Chondrichthyan, 33
prey), Patagonian toothfish \emph{Dissostichus eleginoides}
(Notothenioid fish, 30 prey), and graytail skate \emph{Bathyraja
griseocauda} (Chondrichthyan, 28 prey). Following the same distribution
pattern, few prey presented multiple predators (Figure 3C). The top-five
prey in number of predators were: Detritus (Non-living, 153 predators),
the three categories of Diatoms considered (benthic, centric and
pennate, 72.5 predators on average), and species of the genus
\emph{Euphausia} (Zooplankton, 46 predators). Finally, taking into
account the interactions within each functional group, most interactions
were concentrated in a few species (Figure 3D). The most evident species
were: \emph{Doryteuthis gahi} (Cephalopoda), \emph{Grimothea gregaria}
(Decapoda), \emph{Patagonotothen ramsayi}, \emph{Patagonotothen
guntheri} and \emph{Dissostichus eleginoides} (bentho-pelagic fish),
\emph{Sprattus fuegensis} and \emph{Micromesistius australis} (pelagic
fish), and species of \emph{Euphausia} and \emph{Themisto gaudichaudii}
(Zooplankton). Overall, there is an evident asymmetry in the
distribution of interactions among species at different levels in the
MPA N-BB food web.

@@

Notably, species of mid-TLs (3-4.2) showed the highest values of
betweenness, meaning that those species participated in the highest
number of shortest paths between species (Figure 4A). The following are
the species with the highest values (descending order):
\emph{Patagonotothen ramsayi}, \emph{Salilota australis},
\emph{Dissostichus eleginoides} (fishes), \emph{Doryteuthis gahi}
(Cephalopoda), and \emph{Patagonotothen guntheri} (Notothenioid fish)
(Table S3).

Considering the topological role, `module specialist' species were the
most frequent and presented a wide TL range (1 - 4.78), as well as
`module hub' species (TL = 1 - 3.9); `module connector' was constrained
to mid-TLs (2 - 3.86); and `network connector', was represented by only
one trophic species: detritus (Figure 4D, see Figure S2 for species'
topological roles in a food web graph framework). Here it is important
to highlight the two latter topological roles because they are
responsible for linking modules and maintaining the connectivity of the
food web: 42 species (1 network connector + 41 module connectors) from
19 different functional groups with a TL range = 1 - 3.86. The 41
species with a module connector role represented these functional
groups: Amphipoda, Bivalvia, Brachiopoda, Bryozoa, Hydrozoa (as
`Cnidaria\_benthic'), Copepoda, Cumacea, Decapoda, Echinodermata, fish
(bentho-pelagic and demersal Osteichthyes, and Chondrychthyes),
Foraminifera, Polychaeta, Porifera, Pycnogonida (as `Benthos\_Misc') and
zooplankton (see Supplementary Material Table S3 for the identity of the
species).

@@

\caption{Species-level properties by trophic level: (A) betweenness, (B) closeness, (C) trophic similarity, and (D) topological role. Each point represents a species. Linear regressions for betweenness ($y = 74.82x - 116.82, R^2 = 0.05, p-value < 0.01$), closeness ($y = 1.04e-05x - 9.25e-4, R^2 = 0.004, p-value = 0.11$) and trophic similarity ($y = -0.02x + 0.1 , R^2 = 0.07, p-value < 0.01$). Note that for panels A, B and C only species with TLs equal or greater than 2 were considered.}\label{fig:figure4}
\end{figure}

@@

Food web connectance is a feature that resumes the complexity of the
network, but more importantly, it is an emergent property of pairwise
species interactions (Poisot \& Gravel, 2014). It contains information
regarding how interactions within an ecological network are distributed
and predicts reasonably well key dynamical properties of ecological
networks (Dunne et al., 2002c). Complex marine food webs (i.e.~with more
than 25 trophic species) show connectance values ranging from 0.01 -
0.27 (Marina, Saravia, et al., 2018). In particular, food webs from
high-latitude regions tend to exhibit a connectance closer to the
minimum (between 0.01 and 0.05) (Kortsch et al., 2015; Rodriguez et al.,
2022; Santana et al., 2013). Whether food webs display a low or a high
connectance helps to better comprehend ecosystem's synthetic properties
like robustness. In this sense, empirical analyses support the notion
that highly-connected ecological networks are robust against external
perturbations such as the introduction of new (e.g., invasive) species
(Smith-Ramesh et al., 2017) as well as species removal (e.g., local
extinction) (Dunne et al., 2002a; Montoya \& Solé, 2003). The
connectance of the food web of the MPA Namuncurá - Burdwood Bank (0.01)
is one of the lowest reported so far for these regions; in particular,
it appears to much lower than that of Beagle Channel (0.05), an adjacent
coastal area (Rodriguez et al., 2022).

The degree distribution, the distribution of the number of interactions
per species, is the core of the structure of species interactions, which
influences the opportunities for multiple species to persist in the long
term and, therefore, their coexistence (Godoy et al., 2018). The food
web for the MPA N-BB presents an asymmetric degree distribution. This
pattern was identified at different levels of analysis: food web,
predator, prey, and functional group. Such asymmetry is a well-known
feature in empirical complex food webs in particular (Dunne et al.,
2002c; Montoya \& Solé, 2003; Stouffer et al., 2005), and has received
great attention in complex networks in general (Albert \& Barabási,
2002; Newman, 2003). The degree distribution affects the resilience of
complex food webs against random failures and pressure on a particular
component of the web: food webs showing right-skewed distributions, like
the one described in this study, are more vulnerable to the removal of
the most connected species or hubs, with the potential of producing
secondary extinctions and a catastrophic fragmentation of the network
(Albert et al., 2000; Dunne et al., 2002a; Eklöf \& Ebenman, 2006).

It is suggested that the small-world pattern, i.e., a network with short
path length and high clustering coefficient, is not frequent in complex
marine food webs, mainly due to a low clustering coefficient compared to
random networks (Dunne et al., 2002b; Marina, Saravia, et al., 2018).
However, the food web of the MPA N-BB does display a small-world
pattern. Consequences of this could be of great importance in
recognizing evolutionary paths and the vulnerability to perturbations
(Montoya \& Solé, 2002). On the one hand, a short path length implies a
rapid spread of an impact (e.g., contaminant, population fluctuation,
local extinction) throughout the network but, at the same time, more
potentially adaptive dynamics in the face of external perturbations
(Montoya \& Solé, 2002; Williams et al., 2002). On the other hand, a
high clustering coefficient indicates the formation of subnetworks
composed only by the neighbours of particular species. This translates
into a greater resistance of the network due to the confinement of
perturbations mainly within subnetworks and not spreading between them
(Heer et al., 2020; Kortsch et al., 2019). Overall, a small-world
topology provides ecological networks with greater resilience and
resistance (Bornatowski et al., 2017; Dormann et al., 2017).

@@

The degree distribution allows identifying important species, such as
potential keystone species (Dunne et al., 2002a; Solé \& Montoya, 2001),
generalist/specialist species, and dominant food sources (Kondoh et al.,
2010).

@@

Species' role can also be assessed in a module-based context. Among the
varying numbers of topological roles in which species can be divided,
two are remarkable: `module connector' and `network connector'. Here,
our results point out that there are several species, belonging to a
wide range of trophic positions (1 to 3.86) and representing 17
different functional groups, that should be considered as influential
species for the connectivity of the food web. Thus, we propose that the
diversity of species (benthic and pelagic) maintains the connectivity of
the food web, therefore contributing to the trophic structure and
ecosystem's stability.

@@

\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002}{}}%
Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002a). Network
structure and biodiversity loss in food webs: Robustness increases with
connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567.
\url{https://doi.org/10.1046/j.1461-0248.2002.00354.x}

\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002b}{}}%
Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002b). \emph{Small
{Networks} but not {Small Worlds}: {Unique Aspects} of {Food Web
Structure}}. {Santa Fe Institute}.

\leavevmode\vadjust pre{\hypertarget{ref-Dunne2002a}{}}%
Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002c). Food-web
structure and network theory: {The} role of connectance and size.
\emph{Proceedings of the National Academy of Sciences}, \emph{99}(20),
12917--12922. \url{https://doi.org/10.1073/pnas.192407699}

### 2023-06-29 MS_ToSubmit/SupMaterial.Rmd
Changes on Acanthoserolis & Aega sp

---
title: "Supplementary Material for 'The complex network of trophic interactions in
  a subAntarctic oceanic Marine Protected Area'"
author:
  - Tomás I. Marina
  - Irene R. Schloss
  - Gustavo A. Lovrich
  - Claudia C. Boy
  - Daniel O. Bruno  
  - Fabiana L. Capitanio
  - Sergio M. Delpiani
  - Juan Martín Díaz de Astarloa
  - Cintia Fraysse
  - Virginia A. García Alonso
  - Andrea Raya Rey
  - Mariela L. Spinelli
  - Marcos Tatián
  - Diego Urteaga
  - Luciana Riccialdelli
bibliography: AMPBancoBurdwood.bib
output: pdf_document
---

@@

# Load data
load("../data/cleaned-data_may23.rda")

@@

# Load data
load("../data/cleaned-data_may23.rda")
load("../data/foodweb-data_may23.rda")

@@

Figure 2 shows the species' topological roles in the food web graph. Species, represented by circles, are coloured by role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green). Network connector = 4 species; module connector = 37 species; module hub = 8 species; and module specialist = 326 species.

@@

# Load data
load("../results/summary_results_may23.rda")

>>>>

---
title: "Supplementary Material for 'The complex network of trophic interactions in
  a subAntarctic oceanic Marine Protected Area'"
author:
  - Tomás I. Marina
  - Irene R. Schloss
  - Gustavo A. Lovrich
  - Claudia C. Boy
  - Daniel O. Bruno  
  - Fabiana L. Capitanio
  - Sergio M. Delpiani
  - Juan Martín Díaz de Astarloa
  - Cintia Fraysse
  - Virginia A. García Alonso
  - Andrea Raya Rey
  - Laura Schejter
  - Mariela L. Spinelli
  - Marcos Tatián
  - Diego Urteaga
  - Luciana Riccialdelli
bibliography: AMPBancoBurdwood.bib
output: pdf_document
---

@@

# Load data
load("../data/cleaned-data_jun23.rda")

@@

# Load data
load("../data/cleaned-data_jun23.rda")
load("../data/foodweb-data_jun23.rda")

@@

Figure 2 shows the species' topological roles in the food web graph. Species, represented by circles, are coloured by role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green). Network connector = 1 species; module connector = 41 species; module hub = 10 species; and module specialist = 328 species.

@@

# Load data
load("../results/summary_results_jun23.rda")
